Lifting CDCL to Numerical Domains

### 2016-10-10 example.tex
paper update
CDCL
decision
static analysis equation
example figure added

\section{Working Example}\label{example}
%
\subsection{Example Demonstrating Working of ACDCL}
\begin{figure}[htp]
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{cfg-conflict.pspdftex}}
\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{figure}

\lstdefinestyle{mystyle}{
    numbers=left,                    
    numbersep=5pt,                  
    tabsize=2,
    mathescape=true,
    language=C
}
\lstset{style=mystyle}
Let us consider a simple safe program $P$ as shown in Figure~\ref{fig:filter}A.
Astr{\'e}e fails to verify the safety using interval and trace-partition domain
due to control-flow join at location $n5$.  Astr{\'e}e requires external hints, provided by 
manually annotating the code with partition directives at $n1$, to prove safety.  
In general, the imprecision is either intended by the tool because such high precision analysis is 
normally not required for runtime error analysis or the imprecision is unavoidable 
due to the complexity of the application under analysis.

>>>>

\section{Motivating Example}
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & CFG & Solver Statistics\\
\hline
\begin{lstlisting}[mathescape=true,language=C]
void main() {
 int x,result1=0,result2=0;
 assume(x>=1 && x<= N);
 result1 = 2*x; 
 int state = 1;
 int y=x;
 while(state!=0) {
  switch(state) {
   case 0: state = 1; break;
   case 1: state = 2; break;
   case 2: x--; y++;
   if(x == 0) state = 0;
   else state = 1; break;
  } 
 }
 result2 = y;
 assert(result1 == result2);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{example.pspdftex}}
%\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{minipage}
&
\begin{lstlisting}[mathescape=true,language=C]
                 SAT solver  ACDCL  
restarts           1          0
conflicts  :       5          2
decisions  :       36         2 
propagations :     1365       240  
conflict literals  65         2   
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{C Program, and statistics for decision procedure}
\label{example}
\end{figure}

\begin{figure}[htp]
\centering
\vspace*{0.3cm}
\scalebox{.45}{\import{figures/}{cfg-conflict.pspdftex}}
\caption{A control flow graph for P, P' and abstract conflict graph (ACFG) \label{fig:filter}}
\end{figure}

\Omit {
\lstdefinestyle{mystyle}{
    numbers=left,                    
    numbersep=5pt,                  
    tabsize=2,
    mathescape=true,
    language=C
}
\lstset{style=mystyle}
}
Let us consider a simple safe program $P$ as shown in Figure~\ref{fig:filter}A.
Astr{\'e}e fails to verify the safety using interval and trace-partition domain
due to control-flow join at location $n5$.  Astr{\'e}e requires external hints, provided by 
manually annotating the code with partition directives at $n1$, to prove safety.  
In general, the imprecision is either intended by the tool because such high precision analysis is 
normally not required for runtime error analysis or the imprecision is unavoidable 
due to the complexity of the application under analysis.
